Generating the Blueprints of the Java Ecosystem

### 2015-02-28 msr.tex
changes in 3

Figure~\ref{fig:database-schema} illustrates the database schema. It consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}. The central database table is \textit{measurement}, which holds the measurement values. The other tables are used for normalization.

@@

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them e.g. \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.

Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table. Note that each measurement has a related filename and a related identifier that points to a software element e.g. the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.

Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.

>>>>

Figure~\ref{fig:database-schema} illustrates the database schema. Specifically, it consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}. The central database table is \textit{measurement}, which holds the measurement values. The other tables can be used for normalization.

@@

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them. For instance, \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity generated by the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.

Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table. Note that each measurement has a related filename and a related identifier that points to a software element. For example the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related to the identifier \textit{com.scalagent.jmx}.
Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.
